TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-19 paper/draft.tex
fig 3&4 description

Two tests of consistency were used to assess the validity of our derived test labels: (1) the self-test comparing training labels and test labels, and (2) the leave-one-out cross validation test, in which we train a model on all sources but \emph{n}, then apply the \emph{N-1} source trained model to get the labels for \emph{n}. Precision (scatter) and bias of the model for each test are calculated as the standard deviation and mean of the difference in training and test labels respectively (Figure \ref{fig:mann_validation}).

Another mode of analysis we can look at with \thecannon\ is how the derivative of the model changes with respect to given training parameter, which makes our model interpretable for discovering or verifying atomic or molecular lines with strong dependence on different physical parameters. As discussed further in sections \ref{subsec:mann_results} and \ref{subsec:west_results}, we show the derivative plots of each of our two models and compute the error of the derivative at each pixel using a jackknife statistic:
\begin{equation}
	\sigma_{\theta,m}^2 = \frac{N-1}{N} \sum^N_{n=1} (\theta_{/n}^m - \theta^m)^2 
\end{equation}
where $\sigma_{\theta,m}$ is the error at pixel \emph{m}, \emph{N} is the total number of stars in the sample, indexed by \emph{n}, $\theta$ is the coeffient vector trainined on all N sources, and $\theta_{/n}$ is the coefficient vector trained on \emph{N-1} sources excluding star \emph{n}.

>>>>

Two tests of consistency were used to assess the validity of our derived test labels: (1) the self-test comparing training labels and test labels, and (2) the leave-one-out cross validation (LOOCV) test, in which we train a model on all sources but \emph{n}, then apply the \emph{N-1} source trained model to get the labels for \emph{n}. Precision (scatter) and bias of the model for each test are calculated as the standard deviation and mean of the difference in training and test labels respectively (Figure \ref{fig:mann_validation}).

Another mode of analysis we can look at with \thecannon\ is how the derivative of the model changes with respect to given training parameters, which makes our model interpretable for discovering or verifying atomic or molecular lines with strong dependence on different physical parameters. The top two panels of Figures \ref{fig:demo_teff} and \ref{fig:demo_feh}

The bottom panels of Figures \ref{fig:demo_teff} and \ref{fig:demo_feh} show the derivative of flux with respect to temperature and metallicity at each pixel, taken at the median training values. In order to evaluate which spectral features show statistically significant change with respect to input label, we compute error of the derivative at each pixel using a jackknife statistic (with a 1-$\sigma$ level overplotted in red):
\begin{equation}
	\sigma_{\theta,m}^2 = \frac{N-1}{N} \sum^N_{n=1} (\theta_{/n}^m - \theta^m)^2 
\end{equation}
where $\sigma_{\theta,m}$ is the error at pixel \emph{m}, \emph{N} is the total number of stars in the sample, indexed by \emph{n}, $\theta$ is the coeffient vector trainined on all N sources, and $\theta_{/n}$ is the coefficient vector trained on \emph{N-1} sources excluding star \emph{n}.
